---
title: "Analysis of Interdependent Privacy"
output: html_notebook
---

Importing the dataset.

```{r warning=FALSE}
library(tidyverse)
data <- read_csv('data_24_11_28.csv', show_col_types = FALSE)
head(data)
```

Cleaning the dataset, and removing participants who failed to pass the 
attention checks. Left with 32 participants.
```{r warning=FALSE}
my_data <- data[-1, ]
my_data <- data[-1, ]

my_data <- my_data %>% filter(
  Finished == TRUE, 
  consent == "I agree to take part in the study.",
  age > 17,
  likertscale_help_6 == 2,
  attentioncheck_2 == 7
  )

common_cols <- c(
    'ResponseId',
    'Duration (in seconds)',
    'phoneos',
    'thomashimself_1',
    'thomashimself_2',
    'thomashimself_3',
    'thomasfriend_1',
    'thomasfriend_2',
    'thomasfriend_3',
    'reponsibility_1',
    'reponsibility_2',
    'not_scenario_1',
    'not_scenario_2',
    'not_scenario_3',
    'not_scenario_4',
    'not_scenario_5',
    'not_scenario_6',
    'not_scenario_7',
    'not_scenario_8',
    'accesstoall',
    'apps_number',
    'photos_number',
    'photos_approx',
    'contact_number',
    'contacts_approx',
    'familyevent_number',
    'workevent_number',
    'likertscale_help_1',
    'likertscale_help_2',
    'likertscale_help_3',
    'likertscale_help_4',
    'likertscale_help_5',
    'likertscale_help_7',
    'likertscale_help_8',
    'likertscale_help_9',
    'likertscale_help_10',
    'personalinformation_1',
    'personalinformation_2',
    'personalinformation_3',
    'personalinformation_4',
    'friendinformation_1',
    'friendinformation_2',
    'friendinformation_3',
    'friendinformation_4'
)

survey_data <- my_data %>% select(
  c(mc1_photosperson,
    mc2_photosperson,
    mc1_photosnon,
    mc2_photosnon,
    mc1_contactspersons,
    mc2_contactsperson,
    mc1_contactnonperson,
    mc2_contactnonperson,
    mc1_calendarpersons,
    mc2_calendarperson,
    mc1_calendarnon,
    mc2_calendarnon,
    filesystempersonchec,
    filesystempersonperm,
    qnonpersonfilehave,
    qnonpersonfileperm,
    photo_option_1,
    photo_option_2,
    photo_option_flip_1,
    contact_option_1,
    contact_option_2,
    contact_option_flip_1,
    calendar_option_1,
    calendar_option_2,
    calendar_option_flip_1,
    file_option_1,
    file_option_2,
    file_option_flipped_1,
    photo_paid,
    contact_paid,
    calendar_paid,
    file_paid,
    ),
  common_cols
)

dem_data <- my_data %>% select(
  c(gender,
    ethnicity,
    education,
    education_9_TEXT,
    income,
    usyears,
    yob_1,
    fieldofstudy,
    relationshipstatus,
    children,
    commitmentcheck1,
    commitmentcheck2,
    feedback1,
    feedback2,
    feedback4,
    feedback5,
    feedback6,
    feedback7,)
)

dim(survey_data)
dim(dem_data)
```

Scenario 1 - Photos Persons (5, 4 (correct) participants)
```{r warning=FALSE}
ph_persons <- survey_data %>% select(
  c(mc1_photosperson,
    mc2_photosperson,
    photo_option_1,
    photo_option_2,
    photo_option_flip_1,
    photo_paid
    ),
  common_cols
) %>% filter(mc1_photosperson != "",
             mc2_photosperson != "")

dim(ph_persons)
```

Scenario 2 - Photos Non-Persons (5 participants)
```{r warning=FALSE}
ph_non_persons <- survey_data %>% select(
  c(mc1_photosnon,
    mc2_photosnon,
    photo_option_1,
    photo_option_2,
    photo_option_flip_1,
    photo_paid
    ),
  common_cols
) %>% filter(mc1_photosnon != "",
             mc2_photosnon != "")

dim(ph_non_persons)
```

Scenario 3 - Contacts Persons (3 participants)
```{r warning=FALSE}
cn_persons <- survey_data %>% select(
  c(mc1_contactspersons,
    mc2_contactsperson,
    contact_option_1,
    contact_option_2,
    contact_option_flip_1,
    contact_paid
    ),
  common_cols
) %>% filter(mc1_contactspersons != "",
             mc2_contactsperson != "")

dim(cn_persons)
```

Scenario 4 - Contacts Non-Persons (3, 1 (Correct) participants)
```{r warning=FALSE}
cn_non_persons <- survey_data %>% select(
  c(mc1_contactnonperson,
    mc2_contactnonperson,
    contact_option_1,
    contact_option_2,
    contact_option_flip_1,
    contact_paid
    ),
  common_cols
) %>% filter(mc1_contactnonperson != "",
             mc2_contactnonperson != "")

dim(cn_non_persons)
```

Scenario 5 - Calendar Persons (5 participants)
```{r warning=FALSE}
cl_persons <- survey_data %>% select(
  c(mc1_calendarpersons,
    mc2_calendarperson,
    calendar_option_1,
    calendar_option_2,
    calendar_option_flip_1,
    calendar_paid
    ),
  common_cols
) %>% filter(mc1_calendarpersons != "",
             mc2_calendarperson != "")

dim(cl_persons)
```

Scenario 6 - Calendar Non-Persons (4, 3 (Correct) participants)
```{r warning=FALSE}
cl_non_persons <- survey_data %>% select(
  c(mc1_calendarnon,
    mc2_calendarnon,
    calendar_option_1,
    calendar_option_2,
    calendar_option_flip_1,
    calendar_paid
    ),
  common_cols
) %>% filter(mc1_calendarnon != "",
             mc2_calendarnon != "")

dim(cl_non_persons)
```

Scenario 7 - File System Persons (3, 2 (Correct) participants)
```{r warning=FALSE}
file_persons <- survey_data %>% select(
  c(filesystempersonchec,
    filesystempersonperm,
    file_option_1,
    file_option_2,
    file_option_flipped_1,
    file_paid
    ),
  common_cols
) %>% filter(filesystempersonchec != "",
             filesystempersonperm != "")

dim(file_persons)
```

Scenario 8 - File System Non-Persons (4, 3 (Correct) participants)
```{r warning=FALSE}
file_non_persons <- survey_data %>% select(
  c(qnonpersonfilehave,
    qnonpersonfileperm,
    file_option_1,
    file_option_2,
    file_option_flipped_1,
    file_paid
    ),
  common_cols
) %>% filter(qnonpersonfilehave != "",
             qnonpersonfileperm != "")

dim(file_non_persons)
```

```{r warning=FALSE}
library(ggplot2)

violin_himself <- data.frame(
  name = c(rep("Calendar - Persons", length(cl_persons$thomashimself_1)),
           rep("Calendar - Non-Persons", length(cl_non_persons$thomashimself_1)),
           rep("Contacts - Persons", length(cn_persons$thomashimself_1)),
           rep("Contacts - Non-Persons", length(cn_non_persons$thomashimself_1)),
           rep("Photos - Persons", length(ph_persons$thomashimself_1)),
           rep("Photos - Non-Persons", length(ph_non_persons$thomashimself_1)),
           rep("Files - Persons", length(file_persons$thomashimself_1)),
           rep("Files - Non-Persons", length(file_non_persons$thomashimself_1))),
  value = as.integer(c(cl_persons$thomashimself_1, cl_non_persons$thomashimself_1,
                       cn_persons$thomashimself_1, cn_non_persons$thomashimself_1,
                       ph_persons$thomashimself_1, ph_non_persons$thomashimself_1,
                       file_persons$thomashimself_1, file_non_persons$thomashimself_1))
)

ggplot(violin_himself, aes(x=name, y=value, fill=name)) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks.x=element_blank()) +
  ylab("Concern for Thomas' Privacy") +
  ylim(1, 5) +
  geom_violin(show.legend = F)
  # + geom_boxplot(width = 0.05, alpha = 0.5, show.legend = FALSE)
```


```{r warning=FALSE}
library(ggplot2)

violin_friends <- data.frame(
  name = c(rep("Calendar - Persons", length(cl_persons$thomasfriend_1)),
           rep("Calendar - Non-Persons", length(cl_non_persons$thomasfriend_1)),
           rep("Contacts - Persons", length(cn_persons$thomasfriend_1)),
           rep("Contacts - Non-Persons", length(cn_non_persons$thomasfriend_1)),
           rep("Photos - Persons", length(ph_persons$thomasfriend_1)),
           rep("Photos - Non-Persons", length(ph_non_persons$thomasfriend_1)),
           rep("Files - Persons", length(file_persons$thomasfriend_1)),
           rep("Files - Non-Persons", length(file_non_persons$thomasfriend_1))),
  value = as.integer(c(cl_persons$thomasfriend_1, cl_non_persons$thomasfriend_1,
                       cn_persons$thomasfriend_1, cn_non_persons$thomasfriend_1,
                       ph_persons$thomasfriend_1, ph_non_persons$thomasfriend_1,
                       file_persons$thomasfriend_1, file_non_persons$thomasfriend_1))
)

ggplot(violin_friends, aes(x=name, y=value, fill=name)) +
  theme_classic() +
  theme(axis.title.x = element_blank(),
        axis.ticks.x=element_blank()) +
  ylab("Concern for Privacy for Thomas' Friends") +
  ylim(1, 5) +
  geom_violin(show.legend = F)
  # + geom_boxplot(width = 0.05, alpha = 0.5, show.legend = FALSE)
```

```{r}
a <- survey_data %>% 
  filter(ResponseId %in% c(cn_persons$ResponseId)) %>%
  mutate(permission = "Contacts")

b <- survey_data %>% 
  filter(ResponseId %in% c(ph_persons$ResponseId)) %>%
  mutate(permission = "Photos")

c <- survey_data %>% 
  filter(ResponseId %in% c(cl_persons$ResponseId)) %>%
  mutate(permission = "Calendar")

d <- survey_data %>% 
  filter(ResponseId %in% c(file_persons$ResponseId)) %>%
  mutate(permission = "File System")

persons_himself <- bind_rows(a, b, c, d) %>% 
  select(permission, thomashimself_1, thomashimself_2, thomashimself_3)
persons_himself$group_var <- factor(rep('Persons Himself', 
                                            nrow(persons_himself)))
persons_himself <- persons_himself %>%
  mutate(
    thomashimself_1 = as.integer(thomashimself_1),
    thomashimself_2 = as.integer(thomashimself_2),
    thomashimself_3 = as.integer(thomashimself_3)
  )
names(persons_himself) <-  c('permission', 'question1', 'question2', 'question3', 'group')

persons_friends <- bind_rows(a, b, c, d) %>% 
  select(permission, thomasfriend_1, thomasfriend_2, thomasfriend_3)
persons_friends$group_var <- factor(rep('Persons Friends', 
                                            nrow(persons_friends)))
persons_friends <- persons_friends %>%
  mutate(
    thomasfriend_1 = as.integer(thomasfriend_1),
    thomasfriend_2 = as.integer(thomasfriend_2),
    thomasfriend_3 = as.integer(thomasfriend_3)
  )
names(persons_friends) <- c('permission', 'question1', 'question2', 'question3', 'group')

persons <- bind_rows(persons_himself, persons_friends)

manova_result_persons <- aov(cbind(question1, question2, question3) ~ group, 
                         data = as_tibble(persons))
summary(manova_result_persons)
```

```{r}
a <- survey_data %>% 
  filter(ResponseId %in% c(cn_non_persons$ResponseId)) %>%
  mutate(permission = "Contacts")

b <- survey_data %>% 
  filter(ResponseId %in% c(ph_non_persons$ResponseId)) %>%
  mutate(permission = "Photos")

c <- survey_data %>% 
  filter(ResponseId %in% c(cl_non_persons$ResponseId)) %>%
  mutate(permission = "Calendar")

d <- survey_data %>% 
  filter(ResponseId %in% c(file_non_persons$ResponseId)) %>%
  mutate(permission = "File System")

non_persons_himself <- bind_rows(a, b, c, d) %>% 
  select(permission, thomashimself_1, thomashimself_2, thomashimself_3)
non_persons_himself$group_var <- factor(rep('Non-Persons Himself', 
                                            nrow(non_persons_himself)))
non_persons_himself <- non_persons_himself %>%
  mutate(
    thomashimself_1 = as.integer(thomashimself_1),
    thomashimself_2 = as.integer(thomashimself_2),
    thomashimself_3 = as.integer(thomashimself_3)
  )
names(non_persons_himself) <-  c('permission', 'question1', 'question2', 'question3', 'group')

non_persons_friends <- bind_rows(a, b, c, d) %>% 
  select(permission, thomasfriend_1, thomasfriend_2, thomasfriend_3)
non_persons_friends$group_var <- factor(rep('Non-Persons Friends', 
                                            nrow(non_persons_friends)))
non_persons_friends <- non_persons_friends %>%
  mutate(
    thomasfriend_1 = as.integer(thomasfriend_1),
    thomasfriend_2 = as.integer(thomasfriend_2),
    thomasfriend_3 = as.integer(thomasfriend_3)
  )
names(non_persons_friends) <- c('permission', 'question1', 'question2', 'question3', 'group')

non_persons <- bind_rows(non_persons_himself, non_persons_friends)

manova_result_non <- aov(cbind(question1, question2, question3) ~ group, 
                         data = as_tibble(non_persons))
summary(manova_result_non)
```

```{r}
persons_himself_means <- persons_himself %>%
  group_by(permission) %>%
  summarize(persons_mean_value = round(mean(question1, na.rm = TRUE), 2))

non_persons_himself_means <- non_persons_himself %>%
  group_by(permission) %>%
  summarize(non_persons_mean_value = round(mean(question1, na.rm = TRUE), 2))

himself_means <- non_persons_himself_means %>% inner_join(persons_himself_means)
himself_means
```

```{r}
persons_friends_means <- persons_friends %>%
  group_by(permission) %>%
  summarize(persons_mean_value = round(mean(question1, na.rm = TRUE), 2))

non_persons_friends_means <- non_persons_friends %>%
  group_by(permission) %>%
  summarize(non_persons_mean_value = round(mean(question1, na.rm = TRUE), 2))

friends_means <- non_persons_friends_means %>% inner_join(persons_friends_means)
friends_means
```

```{r}
a <- survey_data %>% 
  filter(ResponseId %in% c(cn_persons$ResponseId)) %>%
  mutate(permission = "Contacts",
         amount = as.numeric(gsub("[^0-9.-]", "", contact_paid)),
         amount = ifelse(is.na(amount), 0, amount)) %>%
  filter(amount > -1) %>%
  select(c(permission, amount))

b <- survey_data %>% 
  filter(ResponseId %in% c(ph_persons$ResponseId)) %>%
  mutate(permission = "Photos",
         amount = as.numeric(gsub("[^0-9.-]", "", photo_paid)),
         amount = ifelse(is.na(amount), 0, amount)) %>%
  filter(amount > -1) %>%
  select(c(permission, amount))

c <- survey_data %>% 
  filter(ResponseId %in% c(cl_persons$ResponseId)) %>%
  mutate(permission = "Calendar",
         amount = as.numeric(gsub("[^0-9.-]", "", calendar_paid)),
         amount = ifelse(is.na(amount), 0, amount)) %>%
  filter(amount > -1) %>%
  select(c(permission, amount))

d <- survey_data %>% 
  filter(ResponseId %in% c(file_persons$ResponseId)) %>%
  mutate(permission = "File System",
         amount = as.numeric(gsub("[^0-9.-]", "", file_paid)),
         amount = ifelse(is.na(amount), 0, amount)) %>%
  filter(amount > -1) %>%
  select(c(permission, amount))

persons_paid_apps <- bind_rows(a, b, c, d)
persons_paid_apps_summary <- persons_paid_apps %>%
  group_by(permission) %>%
  summarize(persons_mean = round(mean(amount, na.rm = TRUE), 2),
            persons_median = round(median(amount, na.rm = TRUE), 2))
persons_paid_apps_summary
```

```{r}
a <- survey_data %>% 
  filter(ResponseId %in% c(cn_non_persons$ResponseId)) %>%
  mutate(permission = "Contacts",
         amount = as.numeric(gsub("[^0-9.-]", "", contact_paid)),
         amount = ifelse(is.na(amount), 0, amount)) %>%
  filter(amount > -1) %>%
  select(c(permission, amount))

b <- survey_data %>% 
  filter(ResponseId %in% c(ph_non_persons$ResponseId)) %>%
  mutate(permission = "Photos",
         amount = as.numeric(gsub("[^0-9.-]", "", photo_paid)),
         amount = ifelse(is.na(amount), 0, amount)) %>%
  filter(amount > -1) %>%
  select(c(permission, amount))

c <- survey_data %>% 
  filter(ResponseId %in% c(cl_non_persons$ResponseId)) %>%
  mutate(permission = "Calendar",
         amount = as.numeric(gsub("[^0-9.-]", "", calendar_paid)),
         amount = ifelse(is.na(amount), 0, amount)) %>%
  filter(amount > -1) %>%
  select(c(permission, amount))

d <- survey_data %>% 
  filter(ResponseId %in% c(file_non_persons$ResponseId)) %>%
  mutate(permission = "File System",
         amount = as.numeric(gsub("[^0-9.-]", "", file_paid)),
         amount = ifelse(is.na(amount), 0, amount)) %>%
  filter(amount > -1) %>%
  select(c(permission, amount))

non_persons_paid_apps <- bind_rows(a, b, c, d)
non_persons_paid_apps_summary <- non_persons_paid_apps %>%
  group_by(permission) %>%
  summarize(non_persons_mean = round(mean(amount, na.rm = TRUE), 2),
            non_persons_median = round(median(amount, na.rm = TRUE), 2))
non_persons_paid_apps_summary
```

```{r}
a <- ph_persons %>%
  mutate(question = as.numeric(thomasfriend_1)) %>%
  select(question)

b <- cn_persons %>%
  mutate(question = as.numeric(thomasfriend_1)) %>%
  select(question)

c <- cl_persons %>%
  mutate(question = as.numeric(thomasfriend_1)) %>%
  select(question)

d <- file_persons %>%
  mutate(question = as.numeric(thomasfriend_1)) %>%
  select(question)

shapiro.test(a$question)
shapiro.test(b$question)
shapiro.test(c$question)
shapiro.test(d$question)
```

```{r}
a <- ph_non_persons %>%
  mutate(question = as.numeric(thomasfriend_1)) %>%
  select(question)

b <- cn_non_persons %>%
  mutate(question = as.numeric(thomasfriend_1)) %>%
  select(question)

c <- cl_non_persons %>%
  mutate(question = as.numeric(thomasfriend_1)) %>%
  select(question)

d <- file_non_persons %>%
  mutate(question = as.numeric(thomasfriend_1)) %>%
  select(question)

shapiro.test(a$question)
shapiro.test(b$question)
shapiro.test(c$question)
shapiro.test(d$question)
```

```{r}
persons_not_sc <- survey_data %>%
  filter((mc1_contactspersons != "" & mc2_contactsperson != "") |
          (mc1_photosperson != "" & mc2_photosperson != "") |
           (mc1_calendarpersons != "" & mc1_calendarpersons != "") |
           (filesystempersonchec != "" & filesystempersonperm != "")) %>%
  select(c(not_scenario_1, not_scenario_2, not_scenario_3, not_scenario_4,
           not_scenario_5, not_scenario_6, not_scenario_7, not_scenario_8))

persons_not_sc <- persons_not_sc %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(persons_not_sc, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(persons_not_sc, 2, median, na.rm = TRUE)

mean_values
median_values
```


```{r}
non_persons_not_sc <- survey_data %>%
  filter((mc1_contactnonperson != "" & mc2_contactnonperson != "") |
          (mc1_photosnon != "" & mc2_photosnon != "") |
           (mc1_calendarnon != "" & mc2_calendarnon != "") |
           (qnonpersonfilehave != "" & qnonpersonfileperm != "")) %>%
  select(c(not_scenario_1, not_scenario_2, not_scenario_3, not_scenario_4,
           not_scenario_5, not_scenario_6, not_scenario_7, not_scenario_8))

non_persons_not_sc <- non_persons_not_sc %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(non_persons_not_sc, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(non_persons_not_sc, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
persons_resp <- survey_data %>%
  filter((mc1_contactspersons != "" & mc2_contactsperson != "") |
          (mc1_photosperson != "" & mc2_photosperson != "") |
           (mc1_calendarpersons != "" & mc2_calendarpersons != "") |
           (filesystempersonchec != "" & filesystempersonperm != "")) %>%
  select(c('reponsibility_1', 'reponsibility_2'))

persons_resp <- persons_resp %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(persons_resp, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(persons_resp, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
non_persons_resp <- survey_data %>%
  filter((mc1_contactnonperson != "" & mc2_contactnonperson != "") |
          (mc1_photosnon != "" & mc2_photosnon != "") |
           (mc1_calendarnon != "" & mc2_calendarnon != "") |
           (qnonpersonfilehave != "" & qnonpersonfileperm != "")) %>%
  select(c('reponsibility_1', 'reponsibility_2'))

non_persons_resp <- non_persons_resp %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(non_persons_resp, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(non_persons_resp, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
cn_persons_install <- survey_data %>%
  filter((mc1_contactspersons != "" & mc2_contactsperson != "")) %>%
  select(c('contact_option_1', 'contact_option_flip_1'))

cn_persons_install <- cn_persons_install %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(cn_persons_install, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(cn_persons_install, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
cn_non_persons_install <- survey_data %>%
  filter((mc1_contactnonperson != "" & mc1_contactnonperson != "")) %>%
  select(c('contact_option_1', 'contact_option_flip_1'))

cn_non_persons_install <- cn_non_persons_install %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(cn_non_persons_install, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(cn_non_persons_install, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
cl_persons_install <- survey_data %>%
  filter((mc1_calendarpersons != "" & mc2_calendarperson != "")) %>%
  select(c('calendar_option_1', 'calendar_option_flip_1'))

cl_persons_install <- cl_persons_install %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(cl_persons_install, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(cl_persons_install, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
ph_persons_install <- survey_data %>%
  filter((mc1_photosperson != "" & mc2_photosperson != "")) %>%
  select(c('photo_option_1', 'photo_option_flip_1'))

ph_persons_install <- ph_persons_install %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(ph_persons_install, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(ph_persons_install, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
ph_non_persons_install <- survey_data %>%
  filter(mc1_photosnon != "" & mc2_photosnon != "") %>%
  select(c('photo_option_1', 'photo_option_flip_1'))

ph_non_persons_install <- ph_non_persons_install %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(ph_non_persons_install, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(ph_non_persons_install, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
file_persons_install <- survey_data %>%
  filter(filesystempersonchec != "" & filesystempersonperm != "") %>%
  select(c('file_option_1', 'file_option_flipped_1'))

file_persons_install <- file_persons_install %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(file_persons_install, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(file_persons_install, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
file_non_persons_install <- survey_data %>%
  filter(qnonpersonfilehave != "" & qnonpersonfileperm != "") %>%
  select(c('file_option_1', 'file_option_flipped_1'))

file_non_persons_install <- file_non_persons_install %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(file_non_persons_install, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(file_non_persons_install, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
persons_twice <- survey_data %>%
  filter((mc1_contactspersons != "" & mc2_contactsperson != "") |
          (mc1_photosperson != "" & mc2_photosperson != "") |
           (mc1_calendarpersons != "" & mc2_calendarperson != "") |
           (filesystempersonchec != "" & filesystempersonperm != "")) %>%
  select(c('personalinformation_2', 'friendinformation_2'))

persons_twice <- persons_twice %>%
  mutate(across(everything(), as.numeric))

# shapiro.test(persons_twice$personalinformation_2)
# shapiro.test(persons_twice$friendinformation_2)
# 
# wilcox_test_result <- wilcox.test(persons_twice$personalinformation_2, 
#                                   persons_twice$friendinformation_2, 
#                                   paired = TRUE)
# 
# wilcox_test_result

mean_values <- apply(persons_twice, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(persons_twice, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
non_persons_twice <- survey_data %>%
  filter((mc1_contactnonperson != "" & mc2_contactnonperson != "") |
          (mc1_photosnon != "" & mc2_photosnon != "") |
           (mc1_calendarnon != "" & mc2_calendarnon != "") |
           (qnonpersonfilehave != "" & qnonpersonfileperm != "")) %>%
  select(c('personalinformation_2', 'friendinformation_2'))

non_persons_twice <- non_persons_twice %>%
  mutate(across(everything(), as.numeric))

mean_values <- apply(non_persons_twice, 2, 
                     function(x) round(mean(x, na.rm = TRUE), 2))
median_values <- apply(non_persons_twice, 2, median, na.rm = TRUE)

mean_values
median_values
```

```{r}
table(dem_data$gender)
table(dem_data$ethnicity)
```

